### 2020-03-16 article_draft.tex
more changes

\documentclass{article}
\usepackage[margin = 0.5in]{geometry}
\usepackage[table]{xcolor}
\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu, setspace, threeparttable,threeparttablex,makecell,natbib, pdfpages}
\usepackage[normalem]{ulem}
\usepackage[english]{babel}
\bibliographystyle{plainnat}

@@

\begin{document} \section{Introduction}
\doublespacing

It is common across scientific disciplines to be interested in predicting an outcome using some (potentially large) number of covariates.  A first step to constructing accurate predictions is to find out if any covariate is associated with the outcome. Testing for the existence of an association can be done with a variety of existing methods, but frequently a trade off must be made between generalizability (ability to use the test for different parameters of interest and data generating mechanisms) and power (ability to detect an association when one exists).  We propose an approach testing for the existence of an association between an outcome and any number of covariates that can be carried out for most parameters of interest that performs nearly as well as tests designed for a specific parameter and data generating mechanism.  We compare our method with other modern methods in a simple simulated data setting.  We then study the tests performance in a setting with a complex sampling scheme, and a setting with a complex parameter of interest.

Back in the day, people used to think about which data to collect.  However, as it became cheaper, more and more data are collected without knowing if any of it can be predictive of the outcome of interest.  We gather many covariates rather than a single one, and whether any of them are predictive is an important first step to using them to do predictions.  It used to be assumed that the covariates we collected were in some way predictive of the outcome.  However, with data collection being so cheep, this is now a question that needs to be answered.

% Multiple hypotheses testing has been an area of interest since at least [].  However finding an elegant

% \sh{In nearly all areas of high-dimensional statistics distinguishing between the important and unimportant predictors is of intrest}. In genetics many candidate snips and their association with some outcome is of interest. Many studies take measurements on a large number of biomarkers to predict medical outcomes such as the presence or progression of a disease. While there has been much focus on finding important predictors, there has been less interest in knowing if any predictors are actually important.  The vast number of potential predictors creates new statistical challenges to answering this less obvious question.

Work with \textcolor{red}{simultaneous hypothesis testing}
%Tests capable of testing the union of multiple hypotheses simultaneously
began with Tukey in 1953 \citep{miller_simultaneous_1981}.  Previous work by Bonferroni was used by \citep{dunn_estimation_1959,dunn_multiple_1961} to come up with some of the first multiple hypothesis testing procedures.  Further improvements were proposed by \citep{hochberg_sharper_1988,holm_simple_1979,s._holland_improved_1988}.  Bonferroni-based correction procedures have the advantage of being easy to apply to already existing tests, while guaranteeing family-wise error control. However because these tests ignore the joint distribution of the test statistics, they suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.

Newer procedures \citep{donoho_higher_2004} and \sh{add other papers here} attain improved power compared to Bonferroni-based methods, but often rely on asymptotics to obtain these results, and don't account for the irregularity of the estimator on which their test is based.  Subsequent work \citep{mckeague_adaptive_2015, pan_powerful_2014, xu_adaptive_2016} addressed these concerns by accounting for the adaptive nature of the considered tests. Still, these newer tests are restricted to testing a particular hypothesis, 
% and test statistic used to test the hypothesis. 
must make assumptions about the data-generating mechanism to obtain theoretical guarantees.

In this article a test is proposed that works across a wide variety of data generating mechanisms and parameters of interest, but also achieves comparable power to tailor made procedures. Section \ref{sec:Working Examples} describes the data generating mechanisms that are considered to evaluate the performance of the test and the competing test made for the given data generating mechanism.  Section \ref{sec:prop_test_proc} proposes the testing procedure. \sh{Add other sections here}  
%This is done using a two step procedure.  In the first step, the limiting distribution of the entire vector of parameter estimates is estimated.  Next, an adaptive procedure selects a transformation of the vector of parameter estimates and distribution which is guessed provides the best power.  P-values are obtained using a permutation procedure.

@@

\section{Proposed Testing Procedure}
\label{sec:prop_test_proc}
For some test statistic $\tst$, any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.  \textcolor{blue}{Let $ \tst \xrightarrow{P_0} \rvv \sim \distv(\disto)$}. This region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
\begin{align}
  Pr_{\distv}\{\rvv \not \in \Theta_0(p)\} = 1 - \alpha \text{ for every } P_0 \in \mathscr{M}_0.\label{eqn:alpha_rej}
\end{align}
While there are many regions satisfying \eqref{eqn:alpha_rej},  we focus for now on a particular class of regions defined using $\ell_p$ norms which will naturally lead to a straightforward testing procedure. For simplicity, \textcolor{blue}{we} first consider regions defined using an $\ell_2$ norm:
\begin{align}
	\Theta_0(r) = \left\{\omega : \|\omega\|_2 \leq r\right\}. \label{eqn:region}
\end{align}
A region satisfying \eqref{eqn:alpha_rej} and \eqref{eqn:region} has a radius defined by: 
% \textcolor{blue}{be consistent on indexing ``$pr$'' -- if you're going to write as $pr_{q(p)}$, do this throughout!}
\begin{align*}
	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}.
\end{align*}
We now construct a test using the region defined above.  Let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$. Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(P)$ when $P$ is contained in the model space  $\mathcal{M}_0$.  Our test can be defined by 
\begin{align}
\label{eqn:simp_test}
	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha,
\end{align} and the corresponding p-values are defined by $
	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.

@@

We can vary any of these three things to give us another test=
The test defined in \eqref{eqn:simp_test} depends on three objects. The first was the chosen norm.  The second was $\sqrt{n}\hat{\boldsymbol{\psi}}$.  The third was the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$.  To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$. Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:

% To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$. Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:

% has the property that $r_\alpha$ will not vary between null distributions. Using this simplification, the result of this test is determined by the norm chosen and the value of the test statistic.

Next consider this procedure in more generality. 
% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
Consider a function $\Gammaf$, of a vector in $\mathbb{R}^d$ (corresponding to $\tst$). While $\Gammaf(x)$ should get larger as $x$ moves away from the null, $\Gammaf$ can be quite general.
%For the example of the $\ell_2$ norm, the p-value calculation was a function of the limiting distribution $Z$ and the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}$
% Because the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under $H_0$ is always a mean zero multivariate normal, we will index our general functions $\Gamma$ by the $d$ by $d$ variance covariance matrix instead of the infinite dimensional distribution function.
%   Under $H_0$, the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ will be a mean zero multivariate normal distribution. 
An example of a more complicated $\Gammaf$ is given below:
% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.  Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.  
% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider 
\begin{align}
	\Gammaf(x) &= Pr_\distv(\|\rvt + x\| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr(\|\rvt\| < c) \geq 0.8 \} \text{ and } \rvt \sim N(0, \Sigma). \label{gamma:pow}
\end{align}
Define the test using $\Gammaf$ as 
\begin{align*}
	\text{reject } H_0 \text{ if } \Gammaf(\tst) > c_{1 - \alpha} \text { where } c_{1 - \alpha} = \min_{c}\{c : \text{Pr}(\Gammaf(Y) \geq c) < \alpha\} \text{ where } Y \sim N(\boldsymbol{0}, \Sigma)
\end{align*}
% \textcolor{blue}{I don't understand the end of this sentence}. 
% While the the above test has nice properties (type one error control, consistency), it is not clear how this test will perform compared to other tests with similar properties.

\begin{figure}
	\centering
	\includegraphics[width = \linewidth]{figure_code/pwr_cmp.jpeg}
	\caption{Plots of 100 observations from a limiting distribution of a hypothetical vector of parameter estimators in $\mathbb{R}^2$ (A) under the null, (B) under an alternative with $\psi_1 = 0, \psi_2 \neq 0$, and (C) under an alternative with $\psi_1, \psi_2 \neq 0$. The 95\% quantiles for the data based on the max (blue) and $\ell_2$ (red) norms under the null are given in all three panels. If a test statistic fell within the purple regions the test would fail to reject $H_0$ if the $\ell_\infty$ norm was used, but would reject $H_0$ if the $\ell_2$ norm was used.  The converse is true for the green regions.  Depending on the alternative, the $\ell_\infty$ norm (B) or the $\ell_2$ norm(C) will achieve higher power.}
	\label{fig:figure1}
\end{figure}

While we have outlined a way of defining different tests of $H_0$, the natural next question is which test will perform the best.  To explore this question, consider a simple example comparing the test described in equation \eqref{eqn:simp_test} with a test that is identical except it uses the maximum absolute value instead of $\ell_2$ norm.  Figure \ref{fig:figure1}, panel (A) illustrates these two tests in $\mathbb{R}^2$. One hundred draws are taken from a bivariate normal distribution with mean zero and identity covariance matrix. All observations in panel (A) except the five with the largest $\ell_2$ norm are contained within the red circle. The blue squares in each panel contains all observations except the five with the largest $\ell_\infty$ norm. 
\textcolor{blue}{The circle and square represent the cutoffs of tests using empirical estimates of the $95^{\text{th}}$ percentile of $\ell_2(\rvt)$ and $\ell_\infty(\rvt)$ respectively.}
Observations that fall within the purple region would result in a rejected null hypothesis if the $\ell_2$ norm was used to define the test, but not if the $\ell_\infty$ norm was used. The converse is true of the green region. Panels B shows draws from an alternative in which $\psi_2 \ne 0$ and $\psi_1 = 0$ and the $\ell_\infty$ norm performs better (achieves higher power). Panel C shows draws from an alternative in which $\psi_1$ and $\psi_2 \neq 0$ and the $\ell_2$ norm performs better.

While both acceptance regions are created so to achieve type $1$ error control, depending on the alternative one test will outperform the other. Panel $B$ shows an alternative in which only $\psi_2$ is non-zero.  Because the max norm only considers the largest coordinate, shifting each observations in only a single direction will have larger impact on the max norm of the observations compared to the $\ell_2$ norm.  This trend is shown by the numerous green observations outside of the blue box (equivalent to rejecting $H_0$) and inside the red circle (equivalent to failing to reject $H_0$). In contrast, there is only a single observation that is outside the red circle, and inside the blue box. The converse trend is shown in panel $C$. Here, the $\ell_2$ norm performs better, because it takes into account both coordinates of the shift whereas the $\ell_\infty$ norm can only take into account one of these coordinate shift.

The efficiency that can be gained from using the correct norm can be quite larger, especially when dimension grows.  Work done by \citep{pinelis_schur2-concavity_2014} states that even for dimensions as small as $3$ the gains in asymptotic efficiency can become arbitrarily large between two potential norms.

@@

\subsection{Adaptive selection of a norm}
In the previous section we showed that a test can be defined with a summarizing function and norm. However, the choice of norm can influence the power of the test. In most scenarios it will not be clear a priori which test will have maximal power for the true alternative. The procedure proposed in this section adaptively selects a norm and it will be shown that this procedure achieves greater power than a test with a fixed norm, while maintaining type 1 error control.

To achieve this, first define $\Gamma_{\Sigma, 1}(x), \dots, \Gamma_{\Sigma, p}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\vmat(x, \|\cdot\|)$, we would define the adaptive version of $\Gamma$ as
\begin{align*}
	\Gammaf^*(x) = \max\left\{\Gamma_{\Sigma, 1}(x), \Gamma_{\Sigma, 2}(x), \dots, \Gamma_{\Sigma, p}(x)\right\}.
\end{align*}
\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

While this function is more complicated than before,  $\Gammaf^*(\rvt)$ can still be compared to $\Gammaf^*(\tst)$ to obtain a p-value. Also, while it may be difficult to obtain the exact distribution of $\Gammaf^*(\rvt)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gammaf^*(\rvt)$ is possible by taking many draws from $\rvt$.

@@

\subsection{Obtaining the null distribution}
\label{ssec:obtaining_null}
The above procedure requires knowledge of the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ when $P \in \mathscr{M}_0$.  To obtain an estimate of this limiting distribution, assume $\sqrt{n}\hat{\boldsymbol{\psi}}$, converges to a normal distribution with an estimable variance covariance matrix when properly centered and normalized. Also assume each of the estimators $\hat{\boldsymbol{\psi}}_1, \dots, \hat{\boldsymbol{\psi}}_d$ of $\boldsymbol{\psi}_1, \dots, \boldsymbol{\psi}_d$ is asymptotically linear.  That is for each $j \in \{1, \dots, d\}$:
\begin{align*}
\hat{\psi}_j = \psi_j + \frac{1}{n}\sum_{i=1}^n D_j(\boldsymbol{x}_i) + o_p(1/\sqrt{n}) \text{ for some function } D_j
\end{align*}
When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo) D(\rvo)^\top \right]$:
% \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$? This is what you would want if $D(\rvo)$ were a column vector, which would be more standard (similar comment in other places where `$\top$' is used)}

\begin{align*}
    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} \rvv \sim N\left(0, \Sigma\right)
\end{align*}
Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximated with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.  In practice, a consistent estimator of $\vmat$, $\hat{\vmat}$ will be used in place of $\vmat$ for the calculation of $\tst$. Thus, the test statistic will be $\Gammaf(\tst)$ will be compared to $\Gammaf(\rvt)$.

@@

\subsection*{Two Phase Sampling Risk Ratio}

>>>>

\documentclass{article}
\usepackage[margin = 1in]{geometry}
\usepackage[table]{xcolor}
\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu, setspace, threeparttable,threeparttablex,makecell,natbib, pdfpages}
\usepackage[normalem]{ulem}
\usepackage[english]{babel}
\bibliographystyle{plainnat}

@@

\begin{document} 
\doublespacing

\begin{abstract}
It is common across scientific disciplines to be interested in predicting an outcome using some (potentially large) number of covariates.  A first step to constructing accurate predictions is to decide if any covariate is associated with the outcome. Testing for the existence of an association can be done with a variety of existing methods, but frequently a trade off is made between generalizability (ability to use the test for different parameters of interest and data generating mechanisms) and power (ability to detect an association when one exists).  We propose an approach testing for the existence of an association between an outcome and any number of covariates that can be carried out for most parameters of interest that performs nearly as well as tests designed for a specific parameter and data generating mechanism.  We compare our method with other modern methods in a simple simulated data setting.  We then study the tests performance in a setting with a complex sampling scheme, and a setting with a complex parameter of interest.  
\end{abstract}

\section{Introduction}

One of the central goals of science is to be able to predict some outcome, often with the help of other related information.  This goal is often attained using the construction of mathematical and statistical models in which many covariates are used to predict the outcome of interest. Because the accuracy of the models is dependent on the presence of an association between the outcome of interest and some number of the covariates it is important to know if any associations exist before attempting to create a model. While this first step is always important, it has become more important as it becomes more common for large numbers of covariates to be collected, often without an explicit outcome of interest in mind.

To test if any covariate is associated with the outcome, a standard approach is to test each covariates association with the outcome. It is desirable for the testing procedure to account for the potentially large number of hypotheses that are simultaneously being tested when using this approach.

Work with \textcolor{red}{simultaneous hypothesis testing}
began with Tukey in 1953 \citep{miller_simultaneous_1981}.  Previous work by Bonferroni was used by \citep{dunn_estimation_1959,dunn_multiple_1961} to come up with some of the first multiple hypothesis testing procedures.  Further improvements were proposed by \citep{hochberg_sharper_1988,holm_simple_1979,s._holland_improved_1988}.  Bonferroni-based correction procedures are easy to apply to already existing tests, while guaranteeing family-wise error control. However because these tests ignore the joint distribution of the test statistics, they suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.

Newer procedures \citep{donoho_higher_2004} and \sh{add other papers here} attain improved power compared to Bonferroni-based methods, but often rely on asymptotics to obtain these results, and don't account for the irregularity of the estimator on which their test is based.  Subsequent work \citep{mckeague_adaptive_2015, pan_powerful_2014, xu_adaptive_2016} addressed these concerns by accounting for the adaptive nature of the considered tests.  While these tests obtain higher power while maintaining type one error control, they were constructed using assumptions about the data generating mechanism, and for only a single measure of association between the outcome of interest and each covariate.  As a result, investigators may still choose to use bonferroni correction based tests if they are interested in a different measure of association or are unsure of how deviations from the assumed data generating mechanism could effect the properties of the testing procedure.

In this article a testing procedure is proposed that can be used for a wide variety of data generating mechanisms and parameters of interest, but also achieves comparable power to tailor made procedures. Section \ref{sec:Working Examples} describes the data generating mechanisms that are considered to evaluate the performance of the test and the competing test made for the given data generating mechanism.  Section \ref{sec:prop_test_proc} proposes the testing procedure. Section \ref{sec:sim_stdy} shows the performance of our testing procedure in the three considered simulation settings. Section \ref{sec:data_app} shows the application of our method to real world data.  Section \ref{sec:discuss} summarizes the findings of this article and notes potential weaknesses and extensions of our procedure.
%This is done using a two step procedure.  In the first step, the limiting distribution of the entire vector of parameter estimates is estimated.  Next, an adaptive procedure selects a transformation of the vector of parameter estimates and distribution which is guessed provides the best power.  P-values are obtained using a permutation procedure.

@@

\section{Proposed Testing Procedure}
\label{sec:prop_test_proc}
For some test statistic $\tst$, any test of $H_0 : \disto \in \mathscr{M}_0$ versus $H_1 : \disto \not\in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$.  Letting $ \tst \xrightarrow{P_0} \rvv \sim \distv(\disto)$ for any $P_0 \in \mathscr{M}_0$, the region $\Theta_0(\disto)$ can be chosen so the probability of rejection under the null is controlled asymptotically:
\begin{align}
  Pr_{\distv}\{\rvv \not \in \Theta_0(P)\} = 1 - \alpha \text{ for every } P_0 \in \mathscr{M}_0.\label{eqn:alpha_rej}
\end{align}
While there are many regions satisfying \eqref{eqn:alpha_rej},  we focus for now on a particular class of regions defined using $\ell_p$ norms which will naturally lead to a straightforward testing procedure. For simplicity, first consider regions defined using an $\ell_2$ norm:
\begin{align}
	\Theta_0(r) = \left\{\omega : \|\omega\|_2 \leq r\right\}. \label{eqn:region}
\end{align}
A region satisfying \eqref{eqn:alpha_rej} and \eqref{eqn:region} has a radius defined by: 
% \textcolor{blue}{be consistent on indexing ``$pr$'' -- if you're going to write as $pr_{q(p)}$, do this throughout!}
\begin{align}
	r_\alpha(\disto) = \min\left\{r : Pr_{\distv}(\|\rvv\|_2 \leq r) \geq 1 - \alpha \right\}. \label{eqn:ra}
\end{align}
To construct a test using the region defined above, let $\hat{\boldsymbol{\Psi}} : \mathbb{R}^d \to \mathbb{R}$ be an estimator of $\boldsymbol{\psi}$, and let $\Hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$. Suppose for now that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to a normal distribution $\distv(P)$ when $P$ is contained in the model space  $\mathcal{M}_0$. The test can be defined by 
\begin{align}
\label{eqn:simp_test}
	\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha(P_0),
\end{align} 
and the corresponding p-values are defined by $
	\text{Pr}_\distv(\|\rvv\|_2 \geq \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2)$.

@@

\begin{figure}
	\centering
	\includegraphics[width = \linewidth]{figure_code/new_pwr_cmpr.jpeg}
	\caption{Plots of 100 observations from a limiting distribution of a hypothetical vector of parameter estimators in $\mathbb{R}^2$ (A) under the null, (B) under an alternative with $\psi_1 = 0, \psi_2 \neq 0$, and (C) under an alternative with $\psi_1, \psi_2 \neq 0$. The 95\% quantiles for the data based on the max (blue) and $\ell_2$ (red) norms under the null are given in all three panels. If a test statistic fell within the blue regions the test would fail to reject $H_0$ if the $\ell_\infty$ norm was used, but would reject $H_0$ if the $\ell_2$ norm was used.  The converse is true for the red regions.  Depending on the alternative, the $\ell_\infty$ norm (B) or the $\ell_2$ norm(C) will achieve higher power.}
	\label{fig:figure1}
\end{figure}

So far, we have outlined a method of constructing a test of $H_0$, but it is easy to imagine other tests defined using different norms. The natural next question is which test will perform the best, and does the choice of norm make a difference.  To explore this question, consider a simple example comparing the test described in equation \eqref{eqn:simp_test} with a test that is identical except it uses the $\ell_\infty$ norm (maximum absolute value) instead of the $\ell_2$ norm.  Figure \ref{fig:figure1}, panel (A) illustrates these two tests in $\mathbb{R}^2$. One hundred draws are taken from $Y$, a bivariate normal distribution with mean zero and identity covariance matrix. All observations in panel (A) except the five with the largest $\ell_2$ norm are contained within the red circle. The blue square contains all observations in panel (A) except the five with the largest $\ell_\infty$ norm.  The circle and square represent the acceptance regions of tests using empirical estimates of the $95^{\text{th}}$ percentile of $\ell_2(\rvt)$ and $\ell_\infty(\rvt)$ respectively corresponding to $r_\alpha(P)$ from \eqref{eqn:ra}.  The same square and circle are redrawn in panels (B) and (C) to illustrate the test's performance under two alternatives. Observations that fall within the blue shaded region would result in a rejected null hypothesis if the $\ell_2$ norm was used to define the test, but not if the $\ell_\infty$ norm was used. The converse is true of the red shaded region. Panels B shows draws from an alternative in which $\psi_2 \ne 0$ and $\psi_1 = 0$ and the $\ell_\infty$ norm performs better (achieves higher power). Panel C shows draws from an alternative in which $\psi_1$ and $\psi_2 \neq 0$ and the $\ell_2$ norm performs better.

While both acceptance regions are created to achieve asymptotic type $1$ error control, depending on the alternative one test will outperform the other. Panel $B$ shows an alternative in which only $\psi_2$ is non-zero.  Because the max norm only considers the largest coordinate, shifting each observation in only a single direction will have larger impact on the max norm of the observations compared to the $\ell_2$ norm.  This trend is shown by the numerous red observations outside of the blue box (equivalent to rejecting $H_0$) and inside the red circle (equivalent to failing to reject $H_0$). In contrast, there is only a single observation that is outside the red circle, and inside the blue box. The converse trend is shown in panel $C$. Here, the $\ell_2$ norm performs better, because it takes into account both coordinates of the shift whereas the $\ell_\infty$ norm can only take into account one of these coordinate shift.

The efficiency that can be gained from using the correct norm can be quite large, especially in high dimension settings.  Work done by \citep{pinelis_schur2-concavity_2014} states that even for dimensions as small as $3$ the gains in asymptotic efficiency for selecting the correct norm can become arbitrarily large between two potential norms \textcolor{blue}{Review this}.

@@

\subsection{Adaptive selection of a norm}
In the previous section we showed that a test can be defined with a summarizing function and norm. However, the choice of norm can influence the power of the test. In many scenarios it will not be clear a priori which test will have maximal power for the true alternative. The procedure proposed in this section adaptively selects a norm and it will be shown that this procedure achieves greater power than a test with a fixed norm, while maintaining type 1 error control.

The test defined in \eqref{eqn:simp_test} is a function of three objects; the chosen norm, $\sqrt{n}\hat{\boldsymbol{\psi}}$, and the limiting distribution of  $\hat{t} = \sqrt{n}\hat{\boldsymbol{\psi}}$. Note that the limiting distribution of $\hat{t}$ under the null will always be a multivariate normal with mean zero with some covariance $\Sigma$. Thus potential tests can be defined using the finite dimensional $\Sigma$ matrix rather than the infinite dimension distribution $Q(P)$.

In order to choose between tests (or norms) it will be important to measures the tests performance in a way that is consistent across norms.  While all tests will reject as the test statistic becomes larger, if the measure of performance was the norm $\hat{t}$ then the optimal norm would always be the $\ell_1$ norm.  To achive this goal, we will consider other mappings from $\mathbb{R}$ into $\mathbb{R}$ that are comparable across norms.  Consider a general function $\Gammaf$, of a vector in $\mathbb{R}^d$ (corresponding to $\tst$). While $\Gammaf(x)$ should get larger as $x$ moves away from the null, $\Gammaf$ can be quite general.
An example of a more complicated $\Gammaf$ is given below:
\begin{align}
	\Gammaf(x) &= Pr_\distv(\|\rvt + x\| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr(\|\rvt\| < c) \geq 0.8 \} \text{ and } \rvt \sim N(0, \Sigma). \label{gamma:pow}
\end{align}
% To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$. Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:

% has the property that $r_\alpha$ will not vary between null distributions. Using this simplification, the result of this test is determined by the norm chosen and the value of the test statistic.
% \subsection{\textcolor{blue}{Creating a rejection region using a function}}

%For the example of the $\ell_2$ norm, the p-value calculation was a function of the limiting distribution $Z$ and the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}$
% Because the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under $H_0$ is always a mean zero multivariate normal, we will index our general functions $\Gamma$ by the $d$ by $d$ variance covariance matrix instead of the infinite dimensional distribution function.
%   Under $H_0$, the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ will be a mean zero multivariate normal distribution. 
% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.  Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.  
% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider

We can define the test using $\Gammaf$ as 
\begin{align*}
	\text{reject } H_0 \text{ if } \Gammaf(\tst) > c_{1 - \alpha} \text { where } c_{1 - \alpha} = \min_{c}\{c : \text{Pr}(\Gammaf(Y) \geq c) < \alpha\} \text{ where } Y \sim N(\boldsymbol{0}, \Sigma)
\end{align*}
% \textcolor{blue}{I don't understand the end of this sentence}. 
% While the the above test has nice properties (type one error control, consistency), it is not clear how this test will perform compared to other tests with similar properties.

Considering the $\Gammaf$ for which it is possible to compare across norms, we can now define a new, adaptive $\Gammaf^*$ which is the pointwise maximum of all of the considered $\Gammaf$'s. First define $\Gamma_{\Sigma, 1}(x), \dots, \Gamma_{\Sigma, p}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\vmat(x, \|\cdot\|)$, we would define the adaptive version of $\Gamma$ as
\begin{align*}
	\Gammaf^*(x) = \max\left\{\Gamma_{\Sigma, 1}(x), \Gamma_{\Sigma, 2}(x), \dots, \Gamma_{\Sigma, p}(x)\right\}.
\end{align*}
\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

While this function is more complicated than before, distribution of $\Gammaf^*(\rvt)$ can still be compared to $\Gammaf^*(\tst)$ to obtain a p-value. Also, while it may be difficult to obtain the exact distribution of $\Gammaf^*(\rvt)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gammaf^*(\rvt)$ is possible by taking many draws from $\rvt$.

@@

\subsection{Obtaining the null distribution}
\label{ssec:obtaining_null}
The described procedure requires knowledge of the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ when $P \in \mathscr{M}_0$.  To obtain an estimate of this limiting distribution, we require that each of the estimators $\hat{\boldsymbol{\psi}}_1, \dots, \hat{\boldsymbol{\psi}}_d$ of $\boldsymbol{\psi}_1, \dots, \boldsymbol{\psi}_d$ is asymptotically linear.  That is for each $j \in \{1, \dots, d\}$:
\begin{align*}
\hat{\psi}_j = \psi_j + \frac{1}{n}\sum_{i=1}^n D_j(\boldsymbol{x}_i) + o_p(1/\sqrt{n}) \text{ for some function } D_j
\end{align*}

Where the $D_j$ function will be referred to as an influence function. While this requirement may seem rigid, most standard measures of association are asymptotically linear, and there exists a rich and growing body of literature that describes asymptotically linear estimators and their corresponding functions \textcolor{blue}{Need citations here}.

% $\sqrt{n}\hat{\boldsymbol{\psi}}$, converges to a normal distribution with an estimable variance covariance matrix when properly centered and normalized.

When there is a fixed number of covariates, the Cramer-Wold device can be used to show that the vector of parameter estimates is asymptotically normal with mean zero, and variance covariance matrix given by $\Sigma = E_{\disto_0}\left[D(\rvo) D(\rvo)^\top \right]$:
% \textcolor{blue}{Note from Alex: do you mean $D(\rvo) D(\rvo)^\top$? This is what you would want if $D(\rvo)$ were a column vector, which would be more standard (similar comment in other places where `$\top$' is used)}

\begin{align*}
    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} \rvv \sim N\left(0, \Sigma\right)
\end{align*}

Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximated with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.  In practice, a consistent estimator of $\vmat$, $\hat{\vmat}$ will be used in place of $\vmat$ for the calculation of $\tst$. Thus, the test statistic will be $\Gammafe(\tst)$ will be compared to $\Gammafe(\rvt)$.

@@

\subsection*{Two Phase Sampling Risk Ratio}
Here, we would expect that the $\ell_2$ norm would perform poorly in the model 2 setting while performing well in the model 3 setting, and that the max norm would perform poorly in the model three setting while performing well in the model two setting.  However, we see the opposite behavior.  Additionally, we find that our adaptive test performs well consistently across all alternatives.
